Calculating Entropies With Nested Sampling

### 2017-01-14 paper/ms.tex
Bibtex file
Conditional entropy

@@

%=================================================================
% References: Variant A
%=================================================================
% Back Matter (References and Notes)
%----------------------------------------------------------
% Style and layout of the references
\bibliographystyle{mdpi}
\makeatletter
\renewcommand\@biblabel[1]{#1. }
\makeatother

%=================================================================
% References:  Variant B
%=================================================================
% Use the following option to include external BibTeX files:
\bibliography{lite}
\bibliographystyle{mdpi}

>>>>

\subsection{The relevance of data}

The degree to which the question ``what is the value of $\x$?'' is
answered by the question ``what is the value of $\d$?'' is given by the
conditional entropy
\begin{align}
H_{\x | \d} &= - \sum_{\d} p(\d) \sum_{\x} p(\x | \d) \log p(\x | \d)
\end{align}
which is the expected value of the entropy of the posterior, averaged over
all possible datasets which might be observed.

\section{Nested Sampling}
Nested Sampling \citep[NS][]{skilling2006nested}

@@

%=================================================================
% References: Variant A
%=================================================================
% Back Matter (References and Notes)
%----------------------------------------------------------
% Style and layout of the references
%\bibliographystyle{mdpi}
\makeatletter
\renewcommand\@biblabel[1]{#1. }
\makeatother

%=================================================================
% References:  Variant B
%=================================================================
% Use the following option to include external BibTeX files:
\bibliographystyle{mdpi}
\bibliography{references}
